---
title: "HTML_Report"
author: "Melissa Edwards"
date: "`r Sys.Date()`"
output: html_document
params:
  show_code: FALSE
  outcome: "Jobs to Nationals"  # Default value
  control: "Sex"               # Default value
  age_poly: 1                  # Default value
  country: "Overall"           # Default value
  plot_data: NULL              
  x3: NULL                     
  x4: NULL                     
  x5: NULL                    
  regression_model: NULL      
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
library(ggplot2)
library(broom)
library(DT)
library(tidyverse)
library(haven)
library(gtsummary)
library(knitr)
```


# Exploration

This section covers exploration of the data used in the regression analysis section below. Outputs entered in the app include country and outcome.

## Outcome Plot
Outcome: `r params$outcome`

Country: `r params$country`

```{r exploration}
req(params$plot_data)
ggplot(params$plot_data, aes(x = age_decade, y = values, fill = variable)) +
  geom_bar(stat = "identity", position = "fill") +
  labs(x = "Age Decade", y = "Percent of Responses", fill = "Level of Agreement",
       title = params$outcome) +
  theme_minimal()

```

## Age Distribution:
```{r}
req(params$x3)
ggplot(params$x3, aes(x = age_decade, y = count)) +
  geom_bar(stat = "identity") +
  labs(x = "Age Decade", y = "Count", title = "Count of Respondent Age by Decade") +
  theme_minimal()
```


## Sex Distribution:
```{r}
req(params$x4)
ggplot(params$x4, aes(x = gender_factor, y = count)) +
  geom_bar(stat = "identity") +
  labs(x = "Gender", y = "Count", title = "Count of Respondent Gender") +
  theme_minimal()
```


## Education Distribution:
```{r}
req(params$x5)
ggplot(params$x5, aes(x = education_factor, y = count)) +
  geom_bar(stat = "identity") +
  labs(x = "Level of Education", y = "Count", title = "Count of Respondent Level of Education") +
  theme_minimal()
```


# Regression

Outcome: `r params$outcome`

Age Polynomial Degree: `r params$age_poly`

Control Variable: `r params$control`


## Regression Summary
```{r}
req(params$regression_model)
summary(params$regression_model)
```


## Regression Coefficients Table
```{r}
req(params$regression_model)
tidy_model <- broom::tidy(params$regression_model, conf.int = TRUE)
knitr::kable(tidy_model, digits = 3, caption = "Regression Coefficients")
```


Residuals vs. Fitted Plot
```{r}
req(params$regression_model)
model_data <- params$regression_model$model
model_data$residuals <- resid(params$regression_model)
model_data$fitted <- fitted(params$regression_model)

ggplot(model_data, aes(x = fitted, y = residuals)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(x = "Fitted Values", y = "Residuals", title = "Residuals vs Fitted Values") +
  theme_minimal()

```

